Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
adding detail to first approach section

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. For this purpose, it assumes some
precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we consider the currently
assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.

>>>>

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$.

We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
independent of the initial states. 
In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria.

We assumes some
precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps.

The safety criteria here must be valid for all possible allowed initial states, and so we 
unwind the transition system $k$ steps, using the previously synthesised $K$, and check that
the state values at each step do not violate the safety bounds for any initial state.

This is relatively computationally expensive if the bounds on the allowed initial states are large. 
However, we can show that, if the controller is safe for each of the corner cases of our hypercube of allowed initial states, 
it is safe for any initial state in the hypercube. Thus we only need to check $2^N$ initial states, where $N$ is the number 
of states.

\todo[inline]{ALESSANDRO: please write out proof that checking only the corner cases is valid for the safety verification}

This check is potentially unsound because we consider the currently
assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.
